Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-06-01 SIOP2024/SIOP2024convergence.tex
Revising "story" for convergence project for SIOP. Unsure if we need the 3rd moderator idea in here, or if it's sufficient as is.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{verbatim}
## Warning: package 'tinylabels' was built under R version 4.1.3
\end{verbatim}

An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001). These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014). Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands. This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.

\begin{figure}
\centering
\includegraphics{SIOP2024convergence_files/figure-latex/uhoh-1.pdf}
\caption{\label{fig:uhoh}Maybe put a hold on this paper as wording of resource and challenge seems very similar}
\end{figure}

see Figure \ref{fig:uhoh}

\hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}

Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}. For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event. One may appraise the nomination as a negative stressor. However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired. Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974). In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000). According to Cavanaugh et al. (2000), challenge demands promote mastery, personal growth, and future gains. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).

Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. Webster et al. (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.

Although it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration. It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.

\hypertarget{current-study-and-hypotheses}{%
\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}

We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances). Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.

\hypertarget{value-of-consulting-onet.}{%
\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}

The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated. These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations. It is also often useful to employers by providing them with information that may be helpful in a job analysis context.

We asked our respondents to select job characteristics that were relevant to them from the broader comprehensive O*Net list. We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources. Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.

\emph{Hypothesis 1}: Characteristics perceived as challenges are also commonly viewed as resources.

Although the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O*Net has different levels of abstraction with regard to the nature of job characteristics. We will be exploring a mid-level abstraction with seven different characteristic scales.

\emph{Research Question 1}: The association between challenging and resourceful characteristics is moderated by type of characteristic.

@@

@@

The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment. The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).

Eligibility requirements included being 18 or older and holding either a full- or part-time job. Participants were asked to think about their primary job while answering the survey. We sampled from a Prolific panel, resulting in 785 individuals who initially accessed the survey link. Of those, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Additional screening using four embedded attention checks resulted in the retention of 568 respondents. A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6\%) or male (46.8\%). Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

We also have ratings of ``\ldots the extent to which this characteristic is present in your job''. Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}. This is probably a better/more appropriate moderator than either of the above two\ldots{}

@@

The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources. Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands. Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand). We did not probe for dependent variable associations, however, Cavanaugh et al. (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al. (2010)). Podsakoff et al. (2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship. Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K.others. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.

\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Demanding Resources}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys. We utilize a set of O*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs. There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.

\hypertarget{not-all-stressors-are-equal-the-challenge-hindrance-framework}{%
\subsection{Not all Stressors are Equal: The Challenge-hindrance Framework}\label{not-all-stressors-are-equal-the-challenge-hindrance-framework}}

Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}. For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event. One may appraise the nomination as a negative stressor. However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired. Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress,'' and ``eustress'' (Selye, 1974). In modern I-O Psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000). According to Cavanaugh et al. (2000), challenge demands promote mastery, personal growth, and future gains. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).

At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes. Research suggests that people can and do perceive them differently. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. Webster et al. (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance. However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow. Using a very wide range of O*Net job characteristics regarding job context and activities, we explore this question:

\emph{RQ1}: Do people distinguish between challenge and hindrance stressors?

\emph{Paired samples t-tests for challenge/hindrance by item?} - I like this first idea. could present it by the 7 different categories.
\emph{Could look}
\emph{Or percent agreement?}
\emph{Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)}

The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources. Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). It stands to reason that a challenging demand may be considered a resource.

\emph{RQ2}: Characteristics perceived as challenges are also commonly viewed as resources.

Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O*Net has different levels of abstraction with regard to the nature of job characteristics. We will be exploring a mid-level abstraction with seven different characteristic scales.

\emph{RQ3}: The association between challenging and resourceful characteristics is moderated by type of characteristic.

We also have ratings of ``\ldots the extent to which this characteristic is present in your job.'' Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}. This is probably a better/more appropriate moderator than either of the above two\ldots{}

@@

Eligibility requirements included being 18 or older and holding either a full- or part-time job. Participants were asked to think about their primary job while answering the survey. We sampled from a Prolific panel, resulting in 785 individuals who initially accessed the survey link. Of those, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Additional screening using four embedded attention checks resulted in the retention of 568 respondents. A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6\%) or male (46.8\%).

@@

The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Following IRB approval, respondents were recruited through Prolific. After providing consent, respondents provided ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work. Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance. The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}). Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

@@

The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources. Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands.

IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like. This is because demands appraised as a challenge promote mastery, personal growth, and future gains. Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).

Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand). We did not probe for dependent variable associations, however, Cavanaugh et al. (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al. (2010)). Podsakoff et al. (2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship. Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-bakker2017job}{}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\hypertarget{ref-bakker2013weekly}{}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\leavevmode\hypertarget{ref-crawford2010linking}{}%
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\leavevmode\hypertarget{ref-demerouti2001job}{}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\hypertarget{ref-peterson2001understanding}{}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., \& others. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\leavevmode\hypertarget{ref-selye1936syndrome}{}%
Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.

\leavevmode\hypertarget{ref-selye1974stress}{}%
Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.

\leavevmode\hypertarget{ref-webster2011extending}{}%
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
